Computer Science House Constitution

### 2025-03-04 constitution.tex
v0.3

\asubsubsection{Renewal of a Root Type Person}
At the conclusion of each academic year, every RTP desiring to maintain their active status for the upcoming academic year must participate in a renewal process. 
During the second to last E-Board Meeting of the semester, the Operational Communications Director shall present a formal statement summarizing the contributions and performance of each RTP. 
After each statement, an E-Board Vote will be conducted to determine each candidate's continuation. 
If the vote does not pass, that member will become a Prior RTP.

>>>>

\asubsubsection{Renewal of a Root Type Person}
At the conclusion of each standard operating session, every RTP desiring to maintain their active status for the upcoming academic year must participate in a renewal process. 
During the second to last E-Board Meeting of the semester, the OpComm Director shall present a formal statement summarizing the contributions and performance of each RTP. 
After each statement, an E-Board Vote, as described in \ref{Executive Board Vote} will be conducted to determine each candidate's continuation. 
Failure to secure the required majority vote will result in the RTP being required to resign their position.
